Probabilistic Programming

### 2014-04-20 paper/paper.tex
Update paper.tex

% overview of markov chain
A primary motivation for undertaking this project was trying to find a new and interesting way to apply a Markov Chain.
A Markov Chain is a stochastic process that uses the current situation and a set of probabilities to determine what 
situation comes next. In the most simple case of a Markov Chain, the next action is based only upon the current situation
and all other previous actions are forgotten. Thus, this process is essentially memoryless because all past states can
be forgotten once a new state is reached. A good example of a Markov Chain is a random walk where at each integer value,
the process chooses a new value such that the two possible values are the current value plus 1 and the current value
minus 1. The transition probabilities for both of these options is .05. This is a good example of a Markov Chain because
the next value on the random walk only depends on the current value in the walk; all previous values are not needed 
to choose the next value \cite{markov}.

>>>>

% overview of markov chain
A primary motivation for undertaking this project was trying to find a new and interesting way to apply a Markov Chain.
A Markov Chain is a stochastic process that uses the current state and a set of probabilities to determine what 
state comes next. In the most simple case of a Markov Chain, the next action is based only upon the current situation
and all other previous actions are forgotten. Thus, this process is essentially memoryless because all past states can
be forgotten once a new state is reached. A good example of a Markov Chain is a random walk where at each integer value,
the process chooses a new value such that the two possible values are the current value plus 1 and the current value
minus 1. The transition probabilities for both of these options is .5. This is a good example of a Markov Chain because
the next value on the random walk only depends on the current value in the walk; all previous values are not needed 
to choose the next value \cite{markov}.
